---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

```

## My mobile notification analysis


```{r}

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vSwjWtfBPrqneiSH5wZiV38Eby1PNUvq6RmK1wMqlQ0Qq1Z5RVD7n_yeyYsyEmDKzJM4KCkAoCEP5-0/pub?output=csv")

latest_data <- logged_data %>%
rename(
app_type = 2,
word_count = 3,
action = 4)

avg_words <- mean(latest_data$word_count, na.rm = TRUE)

total_notifications <- nrow(latest_data)

ggplot(latest_data, aes(x = action)) +
geom_bar(fill = "#003262") +
labs(
title = "Notification processing behavior analysis",
x = "Handling method of this notification",
y = "counts")

ggplot(latest_data, aes(y = app_type, fill = action)) +
geom_bar() +
labs(
title = "Analysis of notification processing behavior of different applications",
subtitle = "Observe which types of app notifications are most easily ignored or clicked.",
x = "Number of notifications",
y = "Application categories",
fill = "Handling method",
caption = "Data source: Personal mobile notification observation logs")
```
```{r}
library(magick)

img_top <- image_read("https://media1.tenor.com/m/pwUWFH15oTMAAAAC/wait.gif") %>%
  image_scale("280x300") %>%
  image_annotate("Me when 10 \nnew emails pops up:", size = 28, color = "#FFFFFF", gravity = "South")

img_bottom <- image_read("https://media1.tenor.com/m/VrxAQ39ypQ8AAAAC/drake-meme-drake.gif") %>%
  image_scale("280x300") %>%
  image_annotate("Me when a \nSocial Media \nnotification pops up:", size = 28, color = "#FFFFFF", gravity = "South")

final_meme <- image_append(c(img_top, img_bottom), stack = TRUE)
print(final_meme)
```

### Personal Phone Notification Analysis Report

This report aims to analyze the frequency of notifications, how I handle them, and whether my handling is related to the different applications the notifications originate from. As shown in the chart 'Analysis of notification processing behavior of different applications', I found that notifications from Social Media were the most likely to be selected as 'Click to view now,' which confirms my tendency to react instantly to social media pushes.

Observation Overview (Dynamic Annotation)

Through analysis of the latest observation records, I found that:

My database currently records a total of `r total_notifications` notification instances.

The average estimated word count for each push notification is approximately `r round(avg_words, 1)`  words.

