---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

```

## My mobile notification analysis

```{r}

suppressPackageStartupMessages(library(tidyverse))
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vSwjWtfBPrqneiSH5wZiV38Eby1PNUvq6RmK1wMqlQ0Qq1Z5RVD7n_yeyYsyEmDKzJM4KCkAoCEP5-0/pub?output=csv")


latest_data <- logged_data %>%
  rename(
    app_type = 'App Category',    
    word_count = 'Estimated word count of the notification content',
    action = 'Handling method of this notification')


avg_words <- mean(latest_data$word_count)
total_notifications <- length(latest_data$app_type)


ggplot(latest_data, aes(x = action)) +
  geom_bar(fill = "#003262") +
  labs(
    title = "Notification processing behavior analysis",
    x = "Handling method of this notification",
    y = "counts"
  )
ggplot(latest_data, aes(y = app_type,fill = action)) +
  geom_bar() +
  labs(
    title = "Analysis of notification processing behavior of different applications",
    subtitle = "Observe which types of app notifications are most easily ignored or clicked.",
    x = "Number of notifications",
    y = "Application categories",
    fill = "Handling method", # Add labels to the illustration
    caption = "Data source: Personal mobile notification observation logs"
  )
```

***Personal Phone Notification Analysis Report***

This report aims to analyze the frequency of notifications, how I handle them, and whether my handling is related to the different applications the notifications originate from.

Observation Overview (Dynamic Annotation)

Through analysis of the latest observation records, I found that:

My database currently records a total of `r total_notifications` notification instances.

The average estimated word count for each push notification is approximately `r round(avg_words, 1)`  words.

